ResultsNPS

### 2019-10-14 R/scripts/resultsNPS.Rmd
cleaning comments and troublesome libraries to install in windows.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('functions/graphs_NPS.R')
source('functions/datasets_NPS.R')
quant_max <- 0.95
size <- params$size

# alternative 1:
# exp_list <- c('IT000125_20190808', 'IT000125_20190812')
# df_original <- compare_sto$get_df_comparison(exp_list)
# df_original %<>% filter(scenario=='numparalleltasks_3' | experiment==1)
# alternative 2:
# compare_sto <- get_compare_sto()
# df_original <- compare_sto$get_instances[[size]]()
# df <- df_original %>% mutate(experiment=if_else(experiment==0, 'cuts', 'base'))
# alternative 3:
df <- do.call(size, args=list())
# df <- get_4_tasks_aggressive()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('functions/graphs_NPS.R')
source('functions/datasets_NPS.R')
quant_max <- 0.95
size <- params$size
df <- do.call(size, args=list())
